Adapting the MVDR to a GPU for active sonar systems of different sizes.

### 2013-01-23 ASA2013/asa2013.tex
la2pdf commit - 2013:01:23	01:03:41	(Wed23.Jan)
la2pdf commit - 2013:01:23	01:34:18	(Wed23.Jan)

\usepackage{tikz}
\usetikzlibrary{shapes,snakes}
\usepackage{amsmath,amssymb}
\usepackage{glossaries}

@@

As we increase system size the inversion step will become more of a bottleneck. Although the dimensionality of the covariance matrix is reduced to $L$ due to subarray averaging, we can reduce it further by performing MVDR beamforming. The underlying concept here that for narrowband data there will be a direct relation between the Fourier transform across the array angles of arrival in the spatial domain; the zero-frequency correspond to broadside, and increasing frequencies map to monotonously increasing opening angles. Since the combined transmit and receive response is highly directive, why would we want to process angles where there are hardly any information?

Beamspace MVDR very closely resembles time domain MVDR. The main difference is the need to Fourier transform the data:
\begin{gather}
\x_\text{BS}[n] = \B\x[n], \qquad \B\in \mathbb{C}^{N_b,M}, \qquad \text{where} \qquad [\B]_{p,q} = \frac{1}{\sqrt{M}} e^{-j2\pi\,p\,q/M}.\label{beamspace}
\end{gather}
$\B$ is usually referred to as 
Complexity: To frequency domain: O($N_b\,L$). Build $R_\text{BS}$, O($N_b^2\,N_L\,N_K$). Inversion: O($N_b^3$).

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,snakes}
\usepackage{amsmath,amssymb}
\usepackage{glossaries}
\usepackage{common/slashbox}

@@

As we increase system size the inversion step will become more of a bottleneck. Although the dimensionality of the covariance matrix is reduced to $L$ due to subarray averaging, we can reduce it further by performing MVDR beamforming. The underlying concept here that for narrowband data there will be a direct relation between the Fourier transform across the array angles of arrival in the spatial domain; the zero-frequency correspond to broadside, and increasing frequencies map to monotonously increasing opening angles. Since the combined transmit and receive response is highly directive, this method allow us to only process the angles where the signal came from.

The beamspace MVDR formulation very closely resembles that of time domain MVDR. The main difference is the initial need to Fourier transform the data:
\begin{gather}
\x_\text{BS}[n] = \B\x[n], \qquad \B\in \mathbb{C}^{N_b,M}, \qquad \text{where} \qquad [\B]_{p,q} = \frac{1}{\sqrt{M}} e^{-j2\pi\,p\,q/M}.\label{beamspace}
\end{gather}
$\B$ here is usually referred to as a Butler matrix. 
Complexity: To frequency domain: O($N_b\,L$). Build $R_\text{BS}$, O($N_b^2\,N_L\,N_K$), Inversion: O($N_b^3$).

@@

\begin{figure}[!h]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/benchmark_tagged.svg}%
\caption{Holmengraa.}\label{mvdr_implementation}
\end{figure}

% \begin{table}[h]\centering%\normalsize
% \begin{tabular}[c]{l r r r@{:}  l}\hline
% \rowcolor{tabBlue} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf BW$_\text{arithmetic}$} & \multicolumn{1}{>{\columncolor{tabBlue}}c}{\bf BW$_\text{memory}$} & \multicolumn{2}{>{\columncolor{tabBlue}}c}{\bf BW$_\text{memory}$/BW$_\text{arithmetic}$} \\\hline
%  & & & & \\
% \end{tabular}
% \caption{Nvidia Quadro 6000; Memory bandwidths (BW) compared to the peak arithmetic bandwidth of 1.03 Tflop/s.}\label{tabbandwidth}
% \end{table}
